---
title: "Lab 10 - Grading the professor, Pt. 2"
author: "Steph Bossert"
date: "13 April"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(tidymodels)
library(openintro)
?evals
view(evals)
```

### Exercise 1-2
### m_bty = 3.88 +.067(bty_avg) 
###Rsq = .04, Adj R sq = .03-- 40% of the variance in scores is explained in this model.
```{r Exercises 1-2}
###1 load data.
m_bty = lm(score~bty_avg, data = evals) #Create the linear regression
summary(m_bty)
```
### m_bty_gen = 3.88 +.07(bty_avg) + (.17)(gender) 
###Exercise 3: Everything else held constant, men score .17 higher than females on their scores
###Ex. 4: 59% of the variance in score is explained by gender and beauty rating...slightly disturbing results...
###Ex 5: m_bty_gen = 3.88 +.07(bty_avg)
###Ex 6: Men
###Ex 7: See plot
###Ex 8: The R square of m_bty_gen is almost 20% percentage points higher, meaning we are accounting for another 20% of variance in scores with the additional information 
###Ex 9: The association/slope increases slightly, yes the addition of gender has changed the slope
###Ex 10: m_bty_rank = 3.98 + .07(bty_avg) -.16(tenure track) -.13(tenure); all else held constant, tenure track professors score .16 points less than tenure professors. All else held constant a one point increase in beauty average is associated with a .07 increase in score. 
```{r multiple regression}
m_bty_gen = lm(score~bty_avg + gender, data = evals)
summary(m_bty_gen)
### m_bty_gen = 3.88 +.07(bty_avg) + (.17)(gender) 
###Exercise 3: Everything else held constant, men score .17 higher than females on their scores
###Ex. 4: 59% of the variance in score is explained by gender and beauty rating...slightly disturbing results...
###Ex 5: m_bty_gen = 3.88 +.07(bty_avg)
###Ex 6: Men
####Ex 7: 
ggplot(evals, aes(x=score, y=bty_avg, group=gender)) + 
  geom_point(shape=18, color="blue")+
  geom_smooth(method=lm, se=FALSE, linetype="solid",
             color="orange") +
  geom_jitter(aes(colour = gender))
m_gen = lm(score~ gender, data = evals)
summary(m_gen)
###Ex 8: The R square of m_bty_gen is almost 20% percentage points higher, meaning we are accounting for another 20% of variance in scores with the additional information 
###Ex 9: The association/slope increases slightly, yes the addition of gender has changed the slope
###Ex 10: 
m_bty_rank = lm(score~bty_avg + rank, data = evals)
summary(m_bty_rank)
### m_bty_rank = 3.98 + .07(bty_avg) -.16(tenure track) -.13(tenure); all else held constant, tenure track professors score 
```
###Ex 11. cls_credits- Class credits
###Ex 12: m_cls = 4.15 + (.48)(cls_credits)
###Ex 13: Do not include cls_did_eval because it would include redundant info in the model and not affect your variance explained in the model
###Ex 14: m_full2= lm(score~ gender + language + age + cls_perc_eval + cls_did_eval + cls_students + cls_level + cls_profs + cls_credits + bty_avg, data=evals)
###Ex 15: m_full9 = lm(score~ gender + ethnicity + bty_avg + rank, data=evals); score = 3.86 +.18(gender) + .10(notminority) .07(bty_avg) -.12(tenure track) - .15(tenure)
###Ex 16: All else held constant, men score .18 points higher than women on average. All others held constant, a 1 point increase in beauty average is associated with an increase in .07 in their scores. 
###Ex 17: Professor would be a non minority man, on the tenure track, who is attractive. 
###Ex 18: I think these results could be generalized to most schools that share similar demographics to the University of Texas. 
```{r Part 3}
###Ex 11. cls_credits- Class credits
###Ex 12
m_cls = lm(score~cls_credits, data = evals)
summary(m_cls)
### m_cls = 4.15 + (.48)(cls_credits)
###Ex 13: Do not include cls_did_eval because it would include redundant info in the model and not affect your variance explained in the model
###Ex 14
m_full2= lm(score~ gender + language + age + cls_perc_eval + cls_did_eval + cls_students + cls_level + cls_profs + cls_credits + bty_avg, data=evals)
###Ex 15:
m_full9 = lm(score~ gender + ethnicity + bty_avg + rank, data=evals)
summary(m_full9)
### score = 3.86 +.18(gender) + .10(notminority) .07(bty_avg) -.12(tenure track) - .15(tenure)
###Ex 16: All else held constant, men score .18 points higher than women on average. All others held constant, a 1 point increase in beauty average is associated with an increase in .07 in their scores. 
###Ex 17: Professor would be a non minority man, on the tenure track, who is attractive. 
###Ex 18: I think these results could be generalized to most schools that share similar demographics to the University of Texas. 
```
